Evaluation of the article

### 2024-10-25 pages/paper_evaluation.qmd
docs(paper evaluation): add previous report checklist, some W.I.P charts, and structure for ISPOR-SDM reflections

@@

<!--TODO: Add a similar thing for whether the article was reporting on/building on analysis using a model previously reported, and cite the paper -->
<!--TODO: In cases where they did, mention whether and what reporting guidelines prior study used -->
<!--TODO: Look at relationship between these two things (prior paper and reporting guidelines) and how many meet -->

@@

>>>>

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  '1 Decision problem': [8, 0, 0, 0],
  '2 Setting/condition': [8, 0, 0, 0],
  '3 Structure': [8, 0, 0, 0],
  '4 Time horizon': [7, 0, 1, 0],
  '5 Scenarios': [7, 0, 0, 1],
  '6 Population': [6, 1, 1, 0],
  '7 Data sources': [8, 0, 0, 0],
  '8 Inputs': [6, 2, 0, 0],
  '9 Uncertainty': [3, 1, 3, 1],
  '10 Sensitivity': [4, 0, 3, 1],
  '11 Face val.': [1, 0, 7, 0],
  '12 Cross val.': [2, 0, 5, 1],
  '13 External val.': [2, 0, 3, 3],
  '14 Predictive val.': [0, 0, 1, 7],
  '15 Generalisability': [5, 1, 2, 0],
  '16 Stakeholders': [1, 0, 7, 0],
  '17 Funding': [6, 0, 2, 0],
  '18 Limitations': [6, 2, 0, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

These guidelines have quite a different focus from STRESS-DES. STRESS-DES is very focused on what and how modelling work is performed. These guidelines do cover that, but have quite alot of focus on validity of the work, and good practice (e.g. stating funding, involving stakeholders).

<!--TODO: Add reflections on each of the elements -->

**1 Is the focused health-related decision problem clarified?**<br>...the decision problem under investigation was defined. DES studies included different types of decision problems, eg, those listed in previously developed taxonomies.

*

**2 Is the modeled healthcare setting/health condition clarified?**<br>...the physical context/scope (eg, a certain healthcare unit or a broader system) or disease spectrum simulated was described.

*

**3 Is the model structure described?**<br>...the model’s conceptual structure was described in the form of either graphical or text presentation.

*

**4 Is the time horizon given?**<br>...the time period covered by the simulation was reported.

*

**5 Are all simulated strategies/scenarios specified?**<br>...the comparators under test were described in terms of their components, corresponding variations, etc

*

**6 Is the target population described?**<br>...the entities simulated and their main attributes were characterized.

*

**7 Are data sources informing parameter estimations provided?**<br>...the sources of all data used to inform model inputs were reported.

*

**8 Are the parameters used to populate model frameworks specified?**<br>...all relevant parameters fed into model frameworks were disclosed.

*

**9 Are model uncertainties discussed?**<br>...the uncertainty surrounding parameter estimations and adopted statistical methods (eg, 95% confidence intervals or possibility distributions) were reported.

*

**10 Are sensitivity analyses performed and reported?**<br>...the robustness of model outputs to input uncertainties was examined, for example via deterministic (based on parameters’ plausible ranges) or probabilistic (based on a priori-defined probability distributions) sensitivity analyses, or both.

*

**11 Is face validity evaluated and reported?**<br>...it was reported that the model was subjected to the examination on how well model designs correspond to the reality and intuitions. It was assumed that this type of validation should be conducted by external evaluators with no stake in the study.

*

**12 Is cross validation performed and reported**<br>...comparison across similar modeling studies which deal with the same decision problem was undertaken.

*

**13 Is external validation performed and reported?**<br>...the modeler(s) examined how well the model’s results match the empirical data of an actual event modeled.

*

**14 Is predictive validation performed or attempted?**<br> ...the modeler(s) examined the consistency of a model’s predictions of a future event and the actual outcomes in the future. If this was not undertaken, it was assessed whether the reasons were discussed.

*

**15 Is the model generalizability issue discussed?**<br>...the modeler(s) discussed the potential of the resulting model for being applicable to other settings/populations (single/multiple application).

*

**16 Are decision makers or other stakeholders involved in modeling?**<br>...the modeler(s) reported in which part throughout the modeling process decision makers and other stakeholders (eg, subject experts) were engaged.

*

**17 Is the source of funding stated?**<br>...the sponsorship of the study was indicated.

* Good practice, usually a journal requirement, although some did not have.

**18 Are model limitations discussed?**<br>...limitations of the assessed model, especially limitations of interest to decision makers, were discussed.

*

@@

@@

<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->

```{python}
import plotly.express as px

# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
previous_stress =  [
  (0, (17/24)*100),
  (0, (14/23)*100),
  (0, (16/21)*100),
  (0, (15/22)*100),
  (0, (14/21)*100),
  (1, (16/19)*100),
  (0, (18/23)*100),
  (1, (22/24)*100)
]

# Get x and y values
x, y = zip(*previous_stress)

fig = px.scatter(x=x, y=y)
fig.show()
```

## Uses a previously reported model

Regarding whether each study was using a previously reported model:

* @shoaib_simulation_2021 - No
* @huang_optimizing_2019 - No
* @lim_staff_2020 - No
* @kim_modelling_2021 - Yes - previously described by @glover_discrete_2018 and @thompson_screening_2018
* @anagnostou_facs-charm_2022 - No
* @johnson_cost_2021 - Yes - `EPIC` model previously described by @sadatsafavi_development_2019
* @hernandez_optimal_2015 - No
* @wood_value_2021 - Yes - previously described by @wood_covid-19_2020

<!--TODO: Add reflections on this, and relationship between these and then e.g. how many of the reporting guidelines were met -->

```{python}
import plotly.express as px

# For each study, define (a) whether use a previously reported model, and (b) proportion of applicable STRESS-DES fully met
previous_stress =  [
  (0, (17/24)*100),
  (0, (14/23)*100),
  (0, (16/21)*100),
  (1, (15/22)*100),
  (0, (14/21)*100),
  (1, (16/19)*100),
  (0, (18/23)*100),
  (1, (22/24)*100)
]

# Get x and y values
x, y = zip(*previous_stress)

fig = px.scatter(x=x, y=y)
fig.show()
```

<!--TODO: Improve this plot so (a) it's not a massive gap between the bars, (b) it's a function used for this and above rather than duplicate code, (c) so we have ones for STRESS and ISPOR -->

<!-- TODO: consider, did the previously reported model also use reporting guidelines? -->
